Modelling BCG vaccination in the UK

### 2019-07-04 rmds/05-evidence-policy-change.Rmd
shortened table and figure captions in lists

```{r model-validation}
comparision_tab[, 1:10] %>% 
  set_names(c("Year of Ending Scheme", rep(c("Original", "Recreated",	"Difference"), 3))) %>% 
  kable(caption = "Comparison of results published by Sutherland et al. vs. the recreated model. This table shows the total notifications including primary and secondary effects from ending the BCG schools' scheme at various times in ethnic White adults aged 15-29 years old in England and Wales.", booktabs = TRUE) %>%
  add_header_above(c(" " = 1, "1988" = 3,  "1993" = 3,  "1998" = 3)) %>% 
  column_spec(1, width = "2cm") %>%
  kable_styling(latex_options = "hold_position") %>% 
  landscape()  %>% 
  kable_styling(font_size = 10) 
```

```{r model-validation-2}
comparision_tab[, -(2:10)] %>% 
  set_names(c("Year of Ending Scheme", rep(c("Original", "Recreated",	"Difference"), 3))) %>% 
  kable(caption = "Continued: Comparison of results published by Sutherland et al. vs. the recreated model. This table shows the total notifications including primary and secondary effects from ending the BCG schools' scheme at various times in ethnic White adults aged 15-29 years old in England and Wales.", booktabs = TRUE) %>%
  add_header_above(c(" " = 1, "2003" = 3,  "2008" = 3, "2013" = 3)) %>% 
  column_spec(1, width = "2cm") %>%
  kable_styling(latex_options = "hold_position") %>% 
  landscape()  %>% 
  kable_styling(font_size = 10) 
```

@@

```{r plot-annual-change, fig.cap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios. For the notification and incidence rate scenarios each line represents the median of 10,000 parameter samples."}
knitr::include_graphics("chapters/evidence-policy-change/plot-annual-change-1.png")
```

@@

```{r graph-vacs-to-prev, fig.cap = "Vaccines required in a cohort of those vaccinated at school-age to prevent a single case of TB within 15 years of vaccination in 2004, 2009, 2014, or 2019. The years presented were dictated by the 5 year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JVCI BCG subgroup, with the addition of a scenario using aggregate notification data and a scenario using estimates of age-specific incidence rates in the UK born. Each boxplot summarises the output of 10,000 model simulations for each scenario. Outliers have been omitted for clarity."}
knitr::include_graphics("chapters/evidence-policy-change/graph-vacs-to-prev-1.png")
```

@@

```{r graph-avg-add-not, fig.cap = "Annual additional notifications in 15-29 year olds from stopping the BCG schools' scheme in 2001, 2006, 2011, and 2016 until 2028. The years presented were dictated by the 5 year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JVCI BCG subgroup, with the addition of a scenario using aggregate notification data and a scenario using estimates of age-specific incidence rates in the UK born. Each boxplot summarises the output of 10,000 model simulations for each scenario. Outliers have been omitted for clarity."}
knitr::include_graphics("chapters/evidence-policy-change/graph-avg-add-nots-1.png")
```

```{r annual-prevent-tab}
  read_formated("tab-annual_nots_prevented") %>% 
  kable(caption = "The median number (with the 2.5\\% and 97.5\\% quantiles) of additional annual notifications due to ending the BCG schools' scheme in selected years.", booktabs = TRUE) %>% 
  landscape() %>% 
  kable_styling(latex_options = "hold_position")  %>% 
  kable_styling(font_size = 8) %>% 
  column_spec(2, width = "2cm")
```

>>>>

```{r model-validation}
comparision_tab[, 1:10] %>% 
  set_names(c("Year of Ending Scheme", rep(c("Original", "Recreated",	"Difference"), 3))) %>% 
  kable(
    caption.short = "Comparison of results published by Sutherland et al. vs. the recreated model.",
    caption = "Comparison of results published by Sutherland et al. vs. the recreated model. This table shows the total notifications including primary and secondary effects from ending the BCG schools' scheme at various times in ethnic White adults aged 15-29 years old in England and Wales.", booktabs = TRUE) %>%
  add_header_above(c(" " = 1, "1988" = 3,  "1993" = 3,  "1998" = 3)) %>% 
  column_spec(1, width = "2cm") %>%
  kable_styling(latex_options = "hold_position") %>% 
  landscape()  %>% 
  kable_styling(font_size = 10) 
```

```{r model-validation-2}
comparision_tab[, -(2:10)] %>% 
  set_names(c("Year of Ending Scheme", rep(c("Original", "Recreated",	"Difference"), 3))) %>% 
  kable(
    caption.short = "Continued: Comparison of results published by Sutherland et al. vs. the recreated model.",
    caption = "Continued: Comparison of results published by Sutherland et al. vs. the recreated model. This table shows the total notifications including primary and secondary effects from ending the BCG schools' scheme at various times in ethnic White adults aged 15-29 years old in England and Wales.", booktabs = TRUE) %>%
  add_header_above(c(" " = 1, "2003" = 3,  "2008" = 3, "2013" = 3)) %>% 
  column_spec(1, width = "2cm") %>%
  kable_styling(latex_options = "hold_position") %>% 
  landscape()  %>% 
  kable_styling(font_size = 10) 
```

@@

```{r plot-annual-change, fig.scap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios.", fig.cap = "Annual percentage change in ethnic White UK born incidence rates for those aged 15-19, 20-24, and 25-29 years old under different scenarios. For the notification and incidence rate scenarios each line represents the median of 10,000 parameter samples.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/plot-annual-change-1.png")
```

@@

```{r graph-vacs-to-prev, fig.scap = "Vaccines required in a cohort of those vaccinated at school-age to prevent a single case of TB within 15 years of vaccination in 2004, 2009, 2014, or 2019.", fig.cap = "Vaccines required in a cohort of those vaccinated at school-age to prevent a single case of TB within 15 years of vaccination in 2004, 2009, 2014, or 2019. The years presented were dictated by the 5 year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JVCI BCG subgroup, with the addition of a scenario using aggregate notification data and a scenario using estimates of age-specific incidence rates in the UK born. Each boxplot summarises the output of 10,000 model simulations for each scenario. Outliers have been omitted for clarity.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/graph-vacs-to-prev-1.png")
```

@@

```{r graph-avg-add-not, fig.scap = "Annual additional notifications in 15-29 year olds from stopping the BCG schools' scheme in 2001, 2006, 2011, and 2016 until 2028.", fig.cap = "Annual additional notifications in 15-29 year olds from stopping the BCG schools' scheme in 2001, 2006, 2011, and 2016 until 2028. The years presented were dictated by the 5 year timestep of the model. The percentage annual decrease scenarios considered were based on those considered by the JVCI BCG subgroup, with the addition of a scenario using aggregate notification data and a scenario using estimates of age-specific incidence rates in the UK born. Each boxplot summarises the output of 10,000 model simulations for each scenario. Outliers have been omitted for clarity.", out.extra = ""}
knitr::include_graphics("chapters/evidence-policy-change/graph-avg-add-nots-1.png")
```

```{r annual-prevent-tab}
  read_formated("tab-annual_nots_prevented") %>% 
  kable(
    caption = "The median number (with the 2.5\\% and 97.5\\% quantiles) of additional annual notifications due to ending the BCG schools' scheme in selected years.", booktabs = TRUE) %>% 
  landscape() %>% 
  kable_styling(latex_options = "hold_position")  %>% 
  kable_styling(font_size = 8) %>% 
  column_spec(2, width = "2cm")
```

### 2019-07-04 rmds/06-tb-bcg-improv-outcomes.Rmd
shortened table and figure captions in lists

table_var_outs[[2]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[2]]) %>% 
    set_names(c('Outcome', 'Years since BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(caption = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated. The baseline exposure is vaccination $\\leq 10$ years before diagnosis compared to vaccination $11+$ years before diagnosis. Deaths due to TB (in those who died) had insufficient data for effect sizes to be estimated in both the univariable and multivariable analysis",
          booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>%  
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape()
```

@@

table_var_outs[[3]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[3]]) %>% 
    set_names(c('Outcome', 'Age at BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(caption = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated - the baseline exposure is vaccination at birth compared to vaccination from 1 to < 12, 12 to < 16, and 16+ years of age.",
         booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                            "* Death due to TB in those who died and where cause of death was known",
                            "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape() %>% 
  {.}
```

@@

```{r 06-imp-bcg}
imp_tab_gen <- function(df = NULL, caption = NULL, escape = TRUE) {
  df %>% 
  kable(caption = caption,
        booktabs = TRUE, escape = escape) %>% 
  column_spec(c(1), width = "3cm") %>%
  add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
  kable_styling(latex_options = "hold_position")
}

@@

```{r 06-imp-yrsincebcg}
sum_imp_yrsinceBCG %>% 
  set_names( c('Outcome', 'OR (95% CI)', 'P-value', 'fmi', 'aOR (95% CI)', 'P-value', 'fmi')) %>% 
  imp_tab_gen(caption = 'Summary of associations between years since vaccination and all outcomes, using pooled imputed data. There was insufficient data to estimate an effect for deaths due to TB (in those who died)') %>% 
  add_header_above(c(" " = 1, "Univariable" = 3, "Multivariable" = 3))
```

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(latex_options = "hold_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    kable_styling(font_size = 8)
```

>>>>

table_var_outs[[2]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[2]]) %>% 
    set_names(c('Outcome', 'Years since BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between years since vaccination and all outcomes in individuals who were vaccinated. The baseline exposure is vaccination $\\leq 10$ years before diagnosis compared to vaccination $11+$ years before diagnosis. Deaths due to TB (in those who died) had insufficient data for effect sizes to be estimated in both the univariable and multivariable analysis",
          booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>%  
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                           "* Death due to TB in those who died and where cause of death was known",
                           "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape()
```

@@

table_var_outs[[3]] %>% 
    combine_model_data_sum(DataSum = ModelDataSum[[3]]) %>% 
    set_names(c('Outcome', 'Age at BCG', 'Cases**', 'Cases with outcome (\\%)', 'OR (95\\% CI)', 'P-value', 'Cases***', 'Cases with outcome (\\%)', 'aOR (95\\% CI)', 'P-value')) %>% 
    kable(
      caption.short = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated.", 
      caption = "Summary of associations between age at vaccination and all outcomes in individuals who were vaccinated - the baseline exposure is vaccination at birth compared to vaccination from 1 to < 12, 12 to < 16, and 16+ years of age.",
         booktabs = TRUE, escape = FALSE) %>% 
    column_spec(c(1, 2, 4, 8), width = "2cm") %>% 
    add_header_above(c(" " = 2, "Univariable" = 4, "Multivariable" = 4)) %>% 
    kable_styling(font_size = 8) %>% 
    kable_styling(latex_options = "hold_position") %>% 
    add_footnote(label = c("OR (95% CI): unadjusted odds ratio with 95% confidence intervals",
                           "aOR (95% CI): adjusted odds ratios with 95% confidence intervals", 
                            "* Death due to TB in those who died and where cause of death was known",
                            "** Univariable sample size for outcomes ordered as in table (% of vaccinated cases) = 8824 (36%), 110 (28%), 9952 (41%), 10018 (41%), 3221 (13%)", 
                           "*** Multivariable sample size with outcomes ordered as in table (% of vaccinated cases) = 7725 (32%), 100 (25%), 8807 (36%), 8855 (36%), 2856 (12%)"
), 
notation = "none") %>% 
  landscape() %>% 
  {.}
```

@@

```{r 06-imp-bcg}
imp_tab_gen <- function(df = NULL, caption = NULL, caption.short = NULL, escape = TRUE) {

  if (is.null(caption.short)) {
    caption.short <- caption
  }

  df %>% 
  kable(
        caption.short = caption.short,
        caption = caption,
        booktabs = TRUE, escape = escape) %>% 
  column_spec(c(1), width = "3cm") %>%
  add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
  kable_styling(latex_options = "hold_position")
}

@@

```{r 06-imp-yrsincebcg}
sum_imp_yrsinceBCG %>% 
  set_names( c('Outcome', 'OR (95% CI)', 'P-value', 'fmi', 'aOR (95% CI)', 'P-value', 'fmi')) %>% 
  imp_tab_gen(
    caption.short = "ummary of associations between years since vaccination and all outcomes, using pooled imputed data.", 
    caption = 'Summary of associations between years since vaccination and all outcomes, using pooled imputed data. There was insufficient data to estimate an effect for deaths due to TB (in those who died)') %>% 
  add_header_above(c(" " = 1, "Univariable" = 3, "Multivariable" = 3))
```

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(
    caption.short = "Summary of associations between BCG vaccination and all outcomes.", 
    caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(latex_options = "hold_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) %>% 
    kable_styling(font_size = 8)
```

### 2019-07-04 rmds/07-direct-effect-bcg-change.Rmd
shortened table and figure captions in lists

```{r 07-cohort-summary-plot, fig.cap = "Mean incidence rates per 100,000, with 95\\% confidence intervals for each retrospective cohort (see Table \\\\@ref(tab:07-cohorts) for cohort definitions), stratified by the vaccination policy and UK birth status. The top and bottom panels are on different scales in order to highlight trends in incidence rates over time."}
knitr::include_graphics("chapters/direct-eff-bcg-change/figure-1.png")
```

@@

make_summary_table <- function(df, caption = NULL) {
  df %>% 
  add_footnote_ref() %>% 
  kable(caption = caption,
        booktabs = TRUE) %>% 
  add_footnote(label = ModelsSummaryFooter, notation = "none") %>% 
  add_header_above(c(" " = 2, "Variable" = 5, " " = 3)) %>% 
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "3cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
}

read_formated("universal-ukborn-results-summary") %>%  
  make_summary_table(caption = paste0("Comparison of models fitted to incidence rates for the UK born population that were relevant to the universal vaccination programme of those at school-age (14). " , ModelOrderingString))
```

@@

df %>% 
  mutate(Variable = replace_indents(Variable)) %>% 
  mutate_all(change_italic_to_latex) %>% 
  mutate(Variable = Variable %>% str_replace_all("\u2020", "**")) %>% 
  kable(caption = paste0("Summary table of incidence rate ratios, in the UK born and non-UK born cohorts relevant to the ", scheme, ", using the best fitting models as determined by comparison of the LOOIC (UK born: ", str_replace(ukborn_model[[2]], "\\.", ""), " (" , ukborn_model[[1]], "), ", "Non-UK born: ", str_replace(nonukborn_model[[2]], "\\.", ""), " (", nonukborn_model[[1]], ")). Model terms which were not included in a given cohort are indicated using a hyphen (-)."), booktabs = TRUE, escape = FALSE) %>% 
  add_footnote(label = c("* Incidence Rate Ratio (95% Credible Interval),",
                         paste0("**There was an improvement in the LOOIC score of ", ukborn_model[[5]]$pretty_diff_looic, " from dropping the change in policy from the model in the UK born cohort and a ", nonukborn_model[[5]]$pretty_diff_looic, " improvement in the non-UK born cohort.")), notation = "none") %>%
  add_header_above(c(" " = 1, "IRR (95% CrI)*" = 2)) %>% 
  add_indent(indents) %>% 
kable_styling(font_size = 8) %>% 
kable_styling(latex_options = "hold_position")
}

@@

```{r 07-summary-universal-nonukborn, results = "asis"}
read_formated("universal-nonukborn-results-summary") %>%
  make_summary_table(caption = paste0("Comparison of models fitted to incidence rates for the non-UK born population that were eligible to the universal vaccination programme of those at school-age (14). ", ModelOrderingString))
```

@@

```{r 07-summary-targeted-ukborn}
read_formated("targeted-ukborn-results-summary") %>%  
  make_summary_table(caption = paste0("Comparison of models fitted to incidence rates for the UK born population that were elgible to the targeted vaccination programme of neonates. ", ModelOrderingString))
```

```{r 07-targeted-tab, results = "asis"}
read_formated("targeted-main-results")  %>% 
  make_combined_table(scheme = "targeted neonatal scheme",
                      ukborn_model = BestFitTargetedUKBorn,
                      nonukborn_model =BestFitTargetedNonUKBorn)
```

```{r 07-summary-targeted-nonukborn, results = "asis"}
read_formated("targeted-nonukborn-results-summary") %>%      
   make_summary_table(caption = paste0("Comparison of models fitted to incidence rates for the non-UK born population that were revelant to the targeted vaccination programme of neonates. ", ModelOrderingString))
```

>>>>

```{r 07-cohort-summary-plot, fig.scap = "Mean incidence rates per 100,000, with 95\\% confidence intervals for each retrospective cohort, stratified by the vaccination policy and UK birth status.", fig.cap = "Mean incidence rates per 100,000, with 95\\% confidence intervals for each retrospective cohort (see Table \\\\@ref(tab:07-cohorts) for cohort definitions), stratified by the vaccination policy and UK birth status. The top and bottom panels are on different scales in order to highlight trends in incidence rates over time.", out.extra = ""}
knitr::include_graphics("chapters/direct-eff-bcg-change/figure-1.png")
```

@@

make_summary_table <- function(df, caption = NULL, caption.short = NULL) {

  if (is.null(caption.short)) {
   caption.short <- caption 
  }

  df %>% 
  add_footnote_ref() %>% 
  kable(
        caption.short = caption.short,
        caption = caption,
        booktabs = TRUE) %>% 
  add_footnote(label = ModelsSummaryFooter, notation = "none") %>% 
  add_header_above(c(" " = 2, "Variable" = 5, " " = 3)) %>% 
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "3cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
}

read_formated("universal-ukborn-results-summary") %>%  
  make_summary_table(
    caption.short = "Comparison of models fitted to incidence rates for the UK born population that were relevant to the universal vaccination programme of those at school-age (14).",
    caption = paste0("Comparison of models fitted to incidence rates for the UK born population that were relevant to the universal vaccination programme of those at school-age (14). " , ModelOrderingString))
```

@@

df %>% 
  mutate(Variable = replace_indents(Variable)) %>% 
  mutate_all(change_italic_to_latex) %>% 
  mutate(Variable = Variable %>% str_replace_all("\u2020", "**")) %>% 
  kable(
    caption.short = paste0("Summary table of incidence rate ratios, in the UK born and non-UK born cohorts relevant to the ", scheme, ", using the best fitting models as determined by comparison of the LOOIC."), 
    caption = paste0("Summary table of incidence rate ratios, in the UK born and non-UK born cohorts relevant to the ", scheme, ", using the best fitting models as determined by comparison of the LOOIC (UK born: ", str_replace(ukborn_model[[2]], "\\.", ""), " (" , ukborn_model[[1]], "), ", "Non-UK born: ", str_replace(nonukborn_model[[2]], "\\.", ""), " (", nonukborn_model[[1]], ")). Model terms which were not included in a given cohort are indicated using a hyphen (-)."), booktabs = TRUE, escape = FALSE) %>% 
  add_footnote(label = c("* Incidence Rate Ratio (95% Credible Interval),",
                         paste0("**There was an improvement in the LOOIC score of ", ukborn_model[[5]]$pretty_diff_looic, " from dropping the change in policy from the model in the UK born cohort and a ", nonukborn_model[[5]]$pretty_diff_looic, " improvement in the non-UK born cohort.")), notation = "none") %>%
  add_header_above(c(" " = 1, "IRR (95% CrI)*" = 2)) %>% 
  add_indent(indents) %>% 
kable_styling(font_size = 8) %>% 
kable_styling(latex_options = "hold_position")
}

@@

```{r 07-summary-universal-nonukborn, results = "asis"}
read_formated("universal-nonukborn-results-summary") %>%
  make_summary_table(
    caption.short = "Comparison of models fitted to incidence rates for the non-UK born population that were eligible to the universal vaccination programme of those at school-age (14).", 
    caption = paste0("Comparison of models fitted to incidence rates for the non-UK born population that were eligible to the universal vaccination programme of those at school-age (14). ", ModelOrderingString))
```

@@

```{r 07-summary-targeted-ukborn}
read_formated("targeted-ukborn-results-summary") %>%  
  make_summary_table(
    caption.short = "Comparison of models fitted to incidence rates for the UK born population that were elgible to the targeted vaccination programme of neonates.", 
    caption = paste0("Comparison of models fitted to incidence rates for the UK born population that were elgible to the targeted vaccination programme of neonates. ", ModelOrderingString))
```

```{r 07-targeted-tab, results = "asis"}
read_formated("targeted-main-results")  %>% 
  make_combined_table(scheme = "targeted neonatal scheme",
                      ukborn_model = BestFitTargetedUKBorn,
                      nonukborn_model = BestFitTargetedNonUKBorn)
```

```{r 07-summary-targeted-nonukborn, results = "asis"}
read_formated("targeted-nonukborn-results-summary") %>%      
   make_summary_table(
     caption.short = "Comparison of models fitted to incidence rates for the non-UK born population that were revelant to the targeted vaccination programme of neonates.", 
     caption = paste0("Comparison of models fitted to incidence rates for the non-UK born population that were revelant to the targeted vaccination programme of neonates. ", ModelOrderingString))
```
